\documentclass[10pt,letterpaper]{article}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[pdfborder={0 0 0}]{hrefhide}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fontawesome}
\usepackage{setspace}


\usepackage[letterpaper,margin=0.8in, footskip=0.25in]{geometry}
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\columnsep}{-.5in}
\pagestyle{empty}

\begin{document}
 % Address is right aligned:
\hspace*{\fill}{\sl (509) 701-9014}	 \vspace{.3pc}\\ 
\hspace*{\fill}{\sl tedfernau@gmail.com} \vspace{.3pc}\\ 
\noindent{\sc \LARGE\bf Theodor Fernau}\hspace*{\fill}\href{http://www.mailaletter.com/}{\sc\sl 213 Bobcat Drive, Ahsahka, ID 83520}\vspace{.3pc}\\ 
%  \hspace*{\fill} {\Large \hrefdisplayonly{https://github.com/tedfernau/}{\faGithubSquare} \quad \hrefdisplayonly{https://www.linkedin.com/in/teddyfernau/}{\faLinkedinSquare}  \quad \hrefdisplayonly{https://twitter.com/tedfernau/}{\faTwitter} \quad \hrefdisplayonly{https://www.instagram.com/theodorfernau/}{\faInstagram} \quad \hrefdisplayonly{https://www.facebook.com/TeddyFernau/}{\faFacebookSquare}}
 \vspace{.3pc}\\ 
 % Draw a horizontal line the whole width of resume:
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

\vspace*{\fill}

{\noindent\sc\bf EXPERIENCE}\vspace{.3pc}\\
\indent\indent		{\bf Embedded Electrical Engineer}	\hspace*{\fill}{ March 2018, current employer} \\
\indent\indent 
{\sl Nightforce Precision Optics, R\&D, Orofino, ID}
				\vspace{0.1in}
                 \begin{itemize}[leftmargin=0.75in, rightmargin=0.25in, topsep=0mm,itemindent=0mm, label=\textrm{--}]
  {\small\sl
\item {\bf Research and Develop electronic systems to enhance precision optics for commercial and military use.} 
\item Develop mixed signal hardware systems from concept to production. My work includes system definition and design, schematic capture, design and layout of printed circuit boards, circuit board assembly and bring-up, hardware testing and debugging.
\item Develop firmware for embedded systems. My work includes low-level peripheral drivers, communications interfaces (BLE, I2C, SPI, UART), processing sensor data, system control, embedded RTOS (FreeRTOS) and firmware system debugging. 
\item Explore the feasibility of integrating electronic technology into optical systems. Produce, interpret, and share research data to guide development efforts. 
\item Act as electronics technician as needed; building, troubleshooting, and fixing electronics.
\item Support legacy products and manufacturing processes including developing electrical testing fixtures, building and troubleshooting such systems. 
}
\end{itemize}

\vspace*{\fill}

{\noindent\sc\bf SKILLS}\vspace{.3pc}\\ 
{\indent\indent\sc\bf Hardware}
 \begin{multicols}{3}
\begin{itemize}[leftmargin=0.75in, rightmargin=0.25in, topsep=0in, itemindent=0in, label=\textrm{--}]
 {\small\sl
\item Altium Designer
\item Prototyping
\item Mixed Signal Design
\item Schematic Capture
\item Circuit Simulation
\item PCB Layout
\item PCB Assembly
\item System Bring-up
\item Hardware Debugging
\item Embedded System Design
\item Electrical Power Systems
\item Consumer Electronics
\item Low Power Design
\item Electronics lab tools
\item Flex-PCBs

}
\end{itemize}
\end{multicols}
{\indent\indent\sc\bf Firmware}
 \begin{multicols}{3}
 \begin{itemize}[leftmargin=0.75in, rightmargin=0.25in, topsep=0mm,itemindent=0mm, label=\textrm{--}]
  {\small\sl
\item  C 
\item Arm Core MCU/MPU
\item Bluetooth Low Energy
\item SPI, I2C, RS-232
\item Embedded RTOS
\item Firmware Debugging
\item UI Design
\item Open Source Toolchains
\item Tortoise SVN
\item Tortoise Git
}
\end{itemize}
\end{multicols}

{\indent\indent\sc\bf Other}
 \begin{multicols}{3}
 \begin{itemize}[leftmargin=0.75in, rightmargin=0.25in, topsep=0mm,itemindent=0mm, label=\textrm{--}]
  {\small\sl
  
\item Professional Communication
\item Technical Writing
\item Collaborative Engineering
\item Engineering Research
\item Customer Service
\item Problem Solving

}
\end{itemize}
\end{multicols}

\vspace*{\fill}

{\noindent\sc\bf EDUCATION and LICENSING}\vspace{.3pc}\\
	\indent\indent{\sl BS,  Electrical Engineering}\hspace*{\fill}{ June 2017}\\
	\indent\indent{\sl BA, Economics}\hspace*{\fill}{\sl Western Washington University} \\
   \indent\indent 
   
	\indent\indent{\sl Engineer in Training}\hspace*{\fill}{ April 2018}\\
	\hspace*{\fill}{ \sl Washington State}
   
    % Draw a horizontal line the whole width of resume:
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
   
\end{document}
